|

### 2023-01-10 paper.Rmd
Tue Jan 10 10:00:09 CET 2023: update-remote.sh

>>>>

<!-- Overview Real World SymReg  -->

To gather more confidence in the previous results, the pre-training strategy for DAE-GP was tested for various real world symbolic regression problems taken from @machine_learning_repo. Are brief summary of the benchmark problems is given in table X

```{r full_run_realWorldSymReg_problems, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
fig.pos="H"
knitr::kable(
  read.csv("./tables/full_run_realWorldSymReg_problems.csv"),
  caption="Overview Real World Symbolic Regression Benchmark Problems"
)%>% row_spec(0,bold=TRUE ) %>% kableExtra::kable_styling(latex_options = "hold_position")
```
Table X summarizes the median best fitness achieved after running each algorithm for 30 runs using a population size of 500 individuals. Statistically significant differences are marked by using asteriks for ($\alpha$) 0.1, 0.05 and 0.01.

```{python createCSV_final_fitness_benchmark}
DIRS=[

]

```{r summarize_final_fitness_benchmarkSymReg, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
fig.pos="H"
knitr::kable(
  read.csv("./tables/full_run_realWorldSymReg_problems.csv"),
  caption="Overview Real World Symbolic Regression Benchmark Problems"
)%>% row_spec(0,bold=TRUE ) %>% kableExtra::kable_styling(latex_options = "hold_position")
```
